---
title: "Regression Models Course Project"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(datasets)
data(mtcars)
```

# Motor Trend Car Analysis

## Executive Summary

Motor Trend magazine, looking at a data set of a collection of cars, is particulary interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

1. “Is an automatic or manual transmission better for MPG”
2. "Quantify the MPG difference between automatic and manual transmissions"

## Data Processing

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

A data frame with 32 observations on 11 variables.

1. mpg	 Miles/(US) gallon
2. cyl	 Number of cylinders
3. disp	 Displacement (cu.in.)
4. hp	 Gross horsepower
5. drat	 Rear axle ratio
6. wt	 Weight (1000 lbs)
7. qsec	 1/4 mile time
8. vs	 V/S
9. am	 Transmission (0 = automatic, 1 = manual)
10. gear	 Number of forward gears
11. carb	 Number of carburetors

## Answering the questions

```{r}
aggregate(mpg~am, data = mtcars, mean)
```

The mean transmission for manual is 7.24mpg higher than automatic.

Now let's try to plot it:

```{r}
boxplot(mpg ~ am, data = mtcars, xlab = "Transmission", ylab = "Miles per gallon", main="Miles per gallon by Transmission Type")
```

Now, let's test whether this difference in mean values is significant:

```{r}
auto <- mtcars[mtcars$am == 0,]
manual <- mtcars[mtcars$am == 1,]
t.test(auto$mpg, manual$mpg)
```

p-value=0.001374. That means that null hypeothesis that difference is not significant is hardly probable.

Now, let's build basic linear regression:

```{r}
fit<-lm(mpg~am,data=mtcars)
summary(fit)
```
We see that automatic transmission runs at 17.147 mpg while manual transmission is 7.245 mpg more. 

However, our R2 is only 0.36 so let's try to add more variables into model: 

```{r}
mvfit <- lm(mpg~am + wt + hp + cyl, data = mtcars)
summary(mvfit)
```

We see that multi-variable model explains 84.9% of variance. 

It may be concluded that on average, manual transmissions have 1.478 more mpg than automatic.

Let's test two models with anova test:

```{r}
anova(fit,mvfit)
```

From the low p-value we see that new model is appropriate. 

## Appendix

```{r}
par(mfrow=c(2, 2))
plot(mvfit)
```

Residuals vs Fitted and Scale-Location plots show no pattern. Normal Q-Q plot indicates that Residuals approximately follow a Normal distributions.

